Supplement to ``{\mytitle}''

### 2023-09-11 si/ReplicateLee20Out.tex
Modified makefile because sed is not the same for mac and linux
Implemented some of Ed's minor suggestions

\caption[Compare to Figure S8 of Lee et al]{Compare to Figure S8 of Lee et al. (2020) supplement.}\label{fig:PlotEpiDist}
\end{figure}

@@

\caption[Bivariate relationships between variables after fitting endemic period]{Bivariate relationships between variables after fitting endemic period. Compare to S9 of Lee et al. (2020) supplement.}\label{fig:plotEndParams}
\end{figure}

@@

\caption[Simulations using parameter sets that were generated by running source code provided by Lee et al (2020)]{Simulations using parameter sets that were generated by running source code provided by Lee et al (2020). Compare to Figure S7 of \cite{lee20sup}. The upper bound for the likelihood of this model is -3031.}\label{fig:plotMod1Sims}
\end{figure}

@@

\end{knitrout}
\caption{\label{fig:mod2rep}
Model 2 trajectories using the \code{haitipkg}. Compare to Figure S15 of \cite{lee20sup}.
}
\end{figure}

@@

\end{knitrout}
\caption{\label{fig:mod3rep}
Simulations from Model~3.
Compare to Figure S18 of \cite{lee20}.
}
\end{figure}

>>>>

\caption[Bivariate distributions of parameter estimates after fitting epidemic phase of the Model~1 following the procedure described by Lee et al]{Bivariate distributions of parameter estimates after fitting epidemic phase of the Model~1 following the procedure described by Lee et al. (2020). Compare to Figure S8 in the supplement of Lee et al. (2020).}\label{fig:PlotEpiDist}
\end{figure}

@@

\caption[Bivariate distributions of parameter estimates after fitting endemic phase of the Model~1 following the procedure described by Lee et al]{Bivariate distributions of parameter estimates after fitting endemic phase of the Model~1 following the procedure described by Lee et al. (2020). Compare to Figure S9 in the supplement of Lee et al. (2020).}\label{fig:plotEndParams}
\end{figure}

@@

\caption[Simulations using parameter sets that were generated by running source code provided by Lee et al (2020)]{Simulations using parameter sets that were generated by running source code provided by Lee et al (2020). Compare to Figure S7 in the supplement of Lee et al. (2020). The upper bound for the likelihood of this model is -3031.}\label{fig:plotMod1Sims}
\end{figure}

@@

\end{knitrout}
\caption{\label{fig:mod2rep}
Model 2 trajectories using the \code{haitipkg}. Compare to Figure S15 in the supplement of \cite{lee20sup}.
}
\end{figure}

@@

\end{knitrout}
\caption{\label{fig:mod3rep}
Simulations from Model~3.
Compare to Figure S18 in the supplement of \cite{lee20}.
}
\end{figure}

### 2023-09-11 si/calibrateMod3.Rnw
Implemented some of Ed's minor suggestions

We refit Model~3 after introducing these hurricane-related parameters using the same successive search scheme described above.
The resulting model has a log-likelihood value of $\Sexpr{round(max(h3_final_results$search2$logLiks$logLik), 1)}$.
The addition of the Hurricane parameters seems to have resulted in a dramatic increase in conditional likelihoods around and after October 2016, as seen in Fig.~\ref{fig:finalCondLL}.
The inclusion of these parameters resulted in an overall increase of $\Sexpr{round(max(h3_final_results$search2$logLiks$logLik) - max(haiti3_sub_fit$search2$logLiks$logLik), 1)}$ log-likelihood units, which is a highly statistically significant difference.

>>>>

We refit Model~3 after introducing these hurricane-related parameters using the same successive search scheme described above.
The resulting model has a log-likelihood value of $\Sexpr{round(max(h3_final_results$search2$logLiks$logLik), 1)}$.
The addition of the Hurricane parameters seems to have resulted in a dramatic increase in conditional likelihoods around and after October 2016, as seen in Fig.~\ref{fig:finalCondLL}.
The inclusion of these parameters resulted in an overall increase of $\Sexpr{round(max(h3_final_results$search2$logLiks$logLik) - max(haiti3_sub_fit$search2$logLiks$logLik), 1)}$ log-likelihood units.
Such a large difference in log-likelihoods is well beyond the threshold of statistical uncertainty determined by Wilks' theorem, suggesting that the data highly favor the inclusion of the additional parameters.

### 2023-09-11 si/calibrateMod3Out.tex
Implemented some of Ed's minor suggestions

We refit Model~3 after introducing these hurricane-related parameters using the same successive search scheme described above.
The resulting model has a log-likelihood value of $-17402.4$.
The addition of the Hurricane parameters seems to have resulted in a dramatic increase in conditional likelihoods around and after October 2016, as seen in Fig.~\ref{fig:finalCondLL}.
The inclusion of these parameters resulted in an overall increase of $157.1$ log-likelihood units, which is a highly statistically significant difference.

>>>>

We refit Model~3 after introducing these hurricane-related parameters using the same successive search scheme described above.
The resulting model has a log-likelihood value of $-17402.4$.
The addition of the Hurricane parameters seems to have resulted in a dramatic increase in conditional likelihoods around and after October 2016, as seen in Fig.~\ref{fig:finalCondLL}.
The inclusion of these parameters resulted in an overall increase of $157.1$ log-likelihood units.
Such a large difference in log-likelihoods is well beyond the threshold of statistical uncertainty determined by Wilks' theorem, suggesting that the data highly favor the inclusion of the additional parameters.
